### 2019-08-03 data/reports.tex
code for draft files

@@

>>>>

Have given this a few days back. Please keep that. The purpose of submitting the form again is to mention some preprints in addition to the one mentioned when I submitted the form a few days ago.

@@

\subsection{Ved Datar}

In collaboration with Adam Jacob and Yuguang Zhang [1], we solved a conjecture of Fukaya's in dimension two, on adiabatic limits of anti-self dual connections on collapsing Calabi-Yau manifolds.   I am also working with Vamsi Pingali on the problem of existence of coupled K\"ahler-Einstein metrics on Fano manifolds. Our preliminary investigations [2] into the problem resulted in the introduction of a more general system of differential equations, christened coupled constant scalar curvature K\"ahler metrics.    [1] Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces. (with Adam Jacob and Yuguang Zhang), preprint,  arXiv:1809.08583, submitted to Journal of Differential Geometry [2]  On coupled constant scalar curvature Kähler metrics (with Vamsi Pingali), preprint,  arXiv:1901.10454, submitted to Journal of Symplectic Geometry
